### 2017-09-26 Sections/foreword.tex
Rohde logos to sketches

Quantum technologies are not just of interest to quantum physicists, but will have transformative effects across countless areas -- the next technological revolution. For this reason, this work is directed at a general audience of not only quantum computer scientists, but also classical computer scientists, physicists, economists, artists, and computer, software and network engineers. More broadly, we hope this work will be of interest to those who recognise the future significance of quantum technologies, and the implications (or even just curiosities) that globally networking them might have.

@@

The entirely technically disinterested or mathematically incompetent reader may refer to just Secs.~\ref{sec:introduction}, \ref{sec:outlook} \& \ref{sec:vision_quant} -- essentially brief non-technical essays about the motivation, applications and implications of the future quantum internet.

>>>>

Quantum technologies\index{Quantum technologies} are not just of interest to quantum physicists, but will have transformative effects across countless areas -- the next technological revolution. For this reason, this work is directed at a general audience of not only quantum computer scientists, but also classical computer scientists, physicists, economists, artists, and computer, software and network engineers. More broadly, we hope this work will be of interest to those who recognise the future significance of quantum technologies, and the implications (or even just curiosities) that globally networking them might have. We expect the answer to that question will look very different to what emerged from the classical internet.

@@

The entirely technically disinterested or mathematically incompetent reader may refer to just Secs.~\ref{sec:introduction}, \ref{sec:outlook} \& \ref{sec:vision_quant} -- essentially brief non-technical, highly speculative essays about the motivation, applications and implications of the future quantum internet.

### 2017-09-26 Sections/the_quantum_space_race.tex
Rohde logos to sketches

\comment{Complete review and editing. Fix citations.}

\comment{Put graphics in correct locations according to referencing. Make sure all are referenced}

\comment{Index this section}

@@

\begin{figure}[!htb]
\includegraphics[width=\columnwidth]{distance_to_horizon}
\caption{Distance to the horizon $d$ (in kilometers), at altitude $h$ (in meters), any several illustrative examples with their elevation. The range for $h$ spans from sea level to roughtly the height of Mount Everest, thereby covering the full range of altitudes possible for ground-based network nodes. However, using more practically realisitic bounds on altitude, say on the order of 5,000-6,000m (already very optimistic!), line-of-sight distance to the horizon will be limited to be on the order of 200-250km. This limitation necessitates the use of repeater networks to enable the efficient approaches for constructing quantum communication channels that bypass this constraint imposed by the Earth's curvature.} \label{fig:dist_hor}
\end{figure}

>>>>

@@

\begin{figure}[!htb]
\includegraphics[width=\columnwidth]{distance_to_horizon}
\caption{Distance to the horizon $d$ (in kilometers), at altitude $h$ (in meters), and several illustrative examples with their elevations. The range for $h$ spans from sea level to roughtly the height of Mount Everest, thereby covering the full range of altitudes possible for ground-based network nodes. However, using more practically realisitic bounds on altitude, say on the order of 5,000-6,000m (already very optimistic!), line-of-sight distance to the horizon will be limited to be on the order of 200-250km. This limitation necessitates the use of repeater networks to enable the efficient approaches for constructing quantum communication channels that bypass this constraint imposed by the Earth's curvature.} \label{fig:dist_hor}
\end{figure}
